\documentclass[12pt]{article}
\usepackage{amssymb}
\title{Homework 4}
\author{Johnny Vastola}
\date{\today}

\begin{document}
\maketitle

\section*{Mathematical Proofs}\\

Prove (or disprove) the following results, showing all steps of your argument.
\begin{enumerate}
\item 
The sum of any two odd integers is even\\
Proof:
Let a and b be odd integers. By definition of odd we have that a = 2n + 1 and
b = 2m + 1. Consider the sum a + b = (2n + 1) + (2m +1) = 2n + 2m +2 = 2k, where k = n + m + 1 is an integer.\\
Therefore by definition of even we have shown that a + b is even
\item
The sum of two even integers is even\\
Proof:
Let a and b be even integers. By definition of even we have that a = 2n and b = 2m.
Consider the sum a + b = 2n + 2m = 2(n + m) = 2k where k = n + m is an integer.\\
Therefore by definition of even we have shown that a + b is even 
\item
The square of an even number is even\\
Proof:
Let n be even $n=2m$, then $n^2=(2m)^2$\\
$n^2 = (2m)^2 = 4m^2
=2(2m^2)$\\
Therefore by definition of even we have shown that $n^2$ is even 
\item
The product of two odd integers is odd\\
Proof:
Let a and b be odd integers. By definition of odd we have that a = 2n + 1
and b = 2m + 1. Consider the product ab = (2n + 1)(2m +1) = 4nm + 2n + 2m +1=
2( 2nm + n + m) + 1 = 2k + 1, where k = (2nm +n +m ) is an integer.\\
Therefore by definition of odd we have shown that the product of two odd integers is also odd. 
\item
If $n^3$+ 5 is odd then n is even, for any  $n \in \mathbb{Z}$\\
Proof: Let n be odd such that n=sk+1 for some integer k\\
Then $n^3+5 =2(4k^3 + 6k^2+ 3k + 3)$\\
Since $n^3 + 5 = 2x $\\
Therefore by definition of even we have shown n is even
\item
If $3n$+ 2 is even then n is even, for any $n \in \mathbb{Z}$\\
Proof: Let n be odd such that n=2k+1 for some integer k\\
3(n)+2=3(2k+1)+2=6k+5=2(3k+2)+1=2(s)+1\\
Therefore by contradiction and the definition of odd we have shown n can be odd
\item
The sum of a rational number and an irrational number is irrational\\
Given:r is a rational number, and x is an irrational number
Suppose r + x is rational.
Since r is rational, −r is also rational; thus the sum of r + x and −r must
be a rational number since the sum of two rational numbers is rational
Thus (r -r) + x = x is rational
Therefore it must not be true that r + x is rational, we have shown that
r + x must be irrational otherwise we would have a contradiction
\item
The product of two irrational numbers is irrational\\
Counterexample: $ \sqrt{2} \times \sqrt{2}=2$

\end{enumerate}

\section*{Basic Counting Principles}\\
Answer the following questions.  Show all steps of your solutions.

\begin{enumerate}
\item
How many different three-letter initials can people have?\\
(A)One has 26 choices for the first initial, 26 for the second, and 26 for the third. Therefore,there are $26 \times 26 \times 26=17576$ possible three-letter initials.
\item
How many different arrangements of the English alphabet are there?\\
(A)There are 26 possibilities for the first letter, 25 for the second... therefore there are 26! arangements.
\item
There are 18 mathematics majors and 325 computer science majors at a college. In how many ways can two representatives be picked so that one is a mathematics major and the other is a computer science major?\\
(A)We must first choose a math major with 18 possibilities. Now
we must choose a CS major with 325 possibilities. Therefore, there are $18 \times 325$ = 5850 possibilities.
\item
A particular brand of shirt comes in 12 colors, has a male version and a female version, and comes in three sizes for each sex.  How many different types of this shirt are made?\\
(A)
Colors=12 Genders=2 Sizes=3\\
12*2*3=72 Therefore there are 72 different types of shirts.
\item
A multiple-choice test contains 10 questions.  There are four possible answers for each question.  In how many ways can a student answer the questions on the test if the student answers every question?\\
(A)There are 4 choices per question, and 10 questions. Choosing an answer for each question is a sequential task, so there are $4 \times 4 \times 4 \times 4 \times 4 \times 4 \times 4 \times 4 \times 4 \times 4 = 1048576$ ways
to answer.
\item
Suppose we have the same multiple choice test as described in question 5, but we relax the assumptionthat the student has to answer all questions.  In other words, how many ways are there for a studentanswer the questions on the test if the student can leave answers blank?\\
(A) There are now 5 choices per question.\\
Therefore,
there are $5 \times 5 \times 5 \times 5 \times 5 \times 5 \times 5 \times 5 \times 5 \times 5 = 9765625$ ways to answer.
\end{enumerate}
\end{document}
